\documentclass[10pt,a4paper]{article}

% -------------------------------------------------------
% ATS CORE
% -------------------------------------------------------
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{microtype}

% -------------------------------------------------------
% FONT — Helvetica
% -------------------------------------------------------
\usepackage[scaled=0.92]{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{xcolor}

% -------------------------------------------------------
% COLORS 
% -------------------------------------------------------
\definecolor{primary}{RGB}{20, 45, 90}
\definecolor{secondary}{RGB}{100, 105, 115}
\definecolor{accent}{RGB}{35, 115, 175}

% -------------------------------------------------------
% LAYOUT — Margini verticali ottimizzati per le nuove righe
% -------------------------------------------------------
\usepackage[margin=1.1cm, top=0.9cm, bottom=0.9cm]{geometry}

% -------------------------------------------------------
% SPACING — Interlinea singola standard
% -------------------------------------------------------
\usepackage{setspace}
\setstretch{1.00}

% -------------------------------------------------------
% SECTION HEADINGS 
% -------------------------------------------------------
\usepackage{titlesec}
\titleformat{\section}
  {\normalsize\bfseries\color{primary}}
  {}{0em}{}
  [\vspace{-0.15em}\color{accent}\rule{\textwidth}{1.0pt}]
\titlespacing{\section}{0pt}{5pt}{3pt}

% -------------------------------------------------------
% LISTS
% -------------------------------------------------------
\usepackage{enumitem}
\setlist[itemize]{
  leftmargin=1.3em, nosep,
  topsep=1pt, itemsep=1pt,
  label=\textcolor{accent}{\textbullet}
}
\setlist[enumerate]{leftmargin=1.3em, nosep, topsep=1pt, itemsep=1pt}

% -------------------------------------------------------
% LINKS
% -------------------------------------------------------
\usepackage[hidelinks]{hyperref}
\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}

\pagestyle{empty}

% -------------------------------------------------------
\begin{document}
% -------------------------------------------------------

% -------------------------------------------------------
% HEADER
% -------------------------------------------------------
\begin{center}
  {\fontsize{22pt}{26pt}\selectfont\textbf{\textcolor{primary}{Alfredo Mungari}}}\\[4pt]
  {\large\textbf{\textcolor{secondary}{Data Scientist \& ML Expert \ \textcolor{accent}{|} \ Software Engineer}}}\\[5pt]
  \small
  \textcolor{secondary}{Naples, Italy}
  \textcolor{accent}{\textbullet}
  \textbf{\textcolor{primary}{+39 333 812 6886}}
  \textcolor{accent}{\textbullet}
  \href{mailto:a.mungari@gmail.com}{\textcolor{accent}{a.mungari@gmail.com}}\\[2pt]
  \href{https://www.linkedin.com/in/alfredo-mungari-99ab9225a}{\textcolor{accent}{LinkedIn}}
  \textcolor{secondary}{\textbullet}
  \href{https://github.com/mungowz}{\textcolor{accent}{GitHub}}
  \textcolor{secondary}{\textbullet}
  \href{https://www.researchgate.net/profile/Alfredo-Mungari-2?ev=hdr_xprf}{\textcolor{accent}{ResearchGate}}
\end{center}

\vspace{2pt}

% -------------------------------------------------------
% PROFESSIONAL PROFILE
% -------------------------------------------------------
\section*{PROFESSIONAL PROFILE}
\noindent\small
Data Scientist specializing in Machine Learning and Generative AI, with research experience at CNR and CI\&SS Lab.
Currently completing an MSc in Applied Computer Science (Machine Learning \& Big Data) at the University of Naples ``Parthenope'',
after graduating BSc with \textbf{110/110 Summa Cum Laude with Special Mention}.
Experienced in collaborative research environments, academic tutoring, and end-to-end ML pipeline development, from data processing to model interpretability.
\normalsize

% -------------------------------------------------------
% PROFESSIONAL EXPERIENCE
% -------------------------------------------------------
\section*{PROFESSIONAL EXPERIENCE}

\noindent
{\normalsize\textbf{\textcolor{primary}{University of Naples ``Parthenope'' (CI\&SS Lab)}}} \hfill \textbf{\small Naples, Italy}\\
{\small\textbf{\textcolor{accent}{Research Intern / Master's Thesis Student}}} \hfill {\small\textit{\textcolor{secondary}{December 2025 -- Present}}}
\begin{itemize}\small
  \item Researching and implementing conditional generative models (\textit{Diffusion Models}) for tabular data generation and manipulation, with applications in synthetic data augmentation.
  \item Developing algorithms for association rule extraction (\textit{Market Basket Analysis}) to identify recurring patterns in large-scale datasets.
  \item Applying Explainable AI (XAI) techniques and Feature Importance analysis to ensure interpretability and transparency of complex predictive models.
\end{itemize}

\vspace{2pt}\noindent
{\normalsize\textbf{\textcolor{primary}{University of Naples ``Parthenope'' (Nola Branch)}}} \hfill \textbf{\small Nola, Italy}\\
{\small\textbf{\textcolor{accent}{Programming Tutor}}} \hfill {\small\textit{\textcolor{secondary}{September 2023 -- July 2025}}}
\begin{itemize}\small
  \item Provided part-time academic support for the BSc in Computer Engineering and Science for Cybersecurity, assisting 30+ students per semester.
  \item Delivered technical assistance and code reviews on programming logic, algorithms, and data structures in C and C++.
\end{itemize}

\vspace{2pt}\noindent
{\normalsize\textbf{\textcolor{primary}{National Research Council (CNR)}}} \hfill \textbf{\small Naples, Italy}\\
{\small\textbf{\textcolor{accent}{Research Intern / Bachelor's Thesis Student}}} \hfill {\small\textit{\textcolor{secondary}{April 2022 -- September 2022}}}
\begin{itemize}\small
  \item Utilized bioinformatics libraries to study molecular interactions for the Bachelor's thesis project.
  \item Designed scripts to fully automate the \textit{molecular docking} process between pesticide ligands and \textit{Apis mellifera} receptors.
\end{itemize}

% -------------------------------------------------------
% EDUCATION
% -------------------------------------------------------
\section*{EDUCATION}

\noindent
{\small\textbf{\textcolor{primary}{University of Naples ``Parthenope''}}} \hfill {\small\textbf{Naples, Italy}}\\
{\small\textbf{Master's Degree in Applied Computer Science} \ \textcolor{secondary}{|} \ \textit{Machine Learning \& Big Data}} \hfill {\small\textit{\textcolor{secondary}{Expected: April 2026}}}

\vspace{3pt}\noindent
{\small\textbf{\textcolor{primary}{University of Naples ``Parthenope''}}} \hfill {\small\textbf{Naples, Italy}}\\
{\small\textbf{Bachelor's Degree in Computer Science}} \hfill {\small\textit{\textcolor{secondary}{December 2022}}}\\
{\footnotesize Grade: \textbf{110/110 Summa Cum Laude with Special Mention} \ \textcolor{secondary}{|} \
Thesis: \href{https://github.com/mungowz/Bachelor-thesis}{\textcolor{accent}{``Molecular interactions \& automation of molecular docking''}} \ \textcolor{secondary}{|} \
\href{https://github.com/mungowz/AUDO4RIAS}{\textcolor{accent}{AUDO4RIAS}}}

\vspace{3pt}\noindent
{\small\textbf{\textcolor{primary}{Liceo Scientifico ``Enrico Medi''}}} \hfill {\small\textbf{Cicciano (NA), Italy}}\\
{\small\textbf{High School Diploma in Scientific Studies}} \hfill {\small\textit{\textcolor{secondary}{Grade: 84/100}}}

% -------------------------------------------------------
% PUBLICATIONS & CONFERENCES
% -------------------------------------------------------
\section*{PUBLICATIONS \& CONFERENCES}
\begin{enumerate}\small
  \item L.~D'Errico et al. \textit{Emotivation in Human-Robot Interaction for Affective Behavioral Adaptation}. In: \textit{Int. Conference on Social Robotics (ICSR+AI)}, 2025. \href{https://www.researchgate.net/publication/399369176_Emotivation_in_Human-Robot_Interaction_for_Affective_Behavioral_Adaptation}{\textcolor{accent}{[ResearchGate]}}
  \item \textit{Attendance:} The 2nd Italian Conference on Big Data and Data Science (ITA DATA), Naples, Sept. 2023.
\end{enumerate}

% -------------------------------------------------------
% SKILLS
% -------------------------------------------------------
\section*{SKILLS}
\begin{itemize}\small
  \item \textbf{\textcolor{primary}{Programming Languages:}} Python, C, C++, SQL, Java, JavaScript, Swift (iOS).
  \item \textbf{\textcolor{primary}{Machine Learning \& Data Science:}} Generative AI (Diffusion Models), PyTorch, scikit-learn, mlxtend, Pandas, NumPy, XAI, Data Mining, Market Basket Analysis, Jupyter Notebook.
  \item \textbf{\textcolor{primary}{GPU \& Parallel Computing:}} CUDA, Multiprocessing.
  \item \textbf{\textcolor{primary}{Tools:}} Git, Conda, Python venv.
  \item \textbf{\textcolor{primary}{Systems:}} Linux, Windows, macOS.
  \item \textbf{\textcolor{primary}{Languages:}} Italian (Native), English (C2 \textcolor{secondary}{|} British Institutes ESOL International).
\end{itemize}

% -------------------------------------------------------
% ADDITIONAL INFO
% -------------------------------------------------------
\section*{ADDITIONAL INFO}
\begin{itemize}\small
  \item \textbf{\textcolor{primary}{Driver's License:}} AM, B (own vehicle).
  \item \textbf{\textcolor{primary}{Courses:}} Apple iOS Foundation Program.
  \item \textbf{\textcolor{primary}{Other:}} Youth Basketball Referee, FIP Campania (2016--2017).
\end{itemize}

% -------------------------------------------------------
\end{document}
